\section*{\centering \Huge \textbf{REFERENCES}}
\vspace{2cm}

\begin{itemize}
\item \textbf{Flask Documentation:} \url{https://flask.palletsprojects.com/}

\item \textbf{React Documentation:} \url{https://react.dev/}

\item \textbf{PostgreSQL Documentation:} \url{https://www.postgresql.org/docs/}

\item \textbf{SQLAlchemy Documentation:} \url{https://www.sqlalchemy.org/}

\item \textbf{Marshmallow Documentation:} \url{https://marshmallow.readthedocs.io/}

\item \textbf{Flask-JWT-Extended Documentation:} \url{https://flask-jwt-extended.readthedocs.io/}

\item \textbf{Vite Documentation:} \url{https://vitejs.dev/}

\item \textbf{Recharts Documentation:} \url{https://recharts.org/}

\item \textbf{Leaflet.js Documentation:} \url{https://leafletjs.com/}

\item \textbf{Docker Documentation:} \url{https://docs.docker.com/}

\item \textbf{ECMWF ERA5 Documentation:} \url{https://www.ecmwf.int/en/forecasts/datasets/reanalysis-datasets/era5}

\item \textbf{OpenWeatherMap API:} \url{https://openweathermap.org/api}

\item \textbf{Google Gemini API Documentation:} \url{https://ai.google.dev/gemini-api/docs}

\item \textbf{OpenAPI Specification:} \url{https://swagger.io/specification/}

\item \textbf{Render Hosting Platform:} \url{https://render.com/}

\item Grinberg, M. (2018). \textit{Flask Web Development: Developing Web Applications with Python} (2nd ed.). O'Reilly Media.

\item Jones, M., Bradley, J., \& Sakimura, N. (2015). \textit{JSON Web Token (JWT)} [RFC 7519]. Internet Engineering Task Force (IETF). Available at: \url{https://datatracker.ietf.org/doc/html/rfc7519}

\item Agresti, A., \& Coull, B. A. (1998). Approximate is Better than "Exact" for Interval Estimation of Binomial Proportions. \textit{The American Statistician}, 52(2), 119-126.

\item Wilson, E. B. (1927). Probable Inference, the Law of Succession, and Statistical Inference. \textit{Journal of the American Statistical Association}, 22(158), 209-212.

\item Gelman, A., Carlin, J. B., Stern, H. S., Dunson, D. B., Vehtari, A., \& Rubin, D. B. (2013). \textit{Bayesian Data Analysis} (3rd ed.). CRC Press.

\item Dwork, C., \& Roth, A. (2014). The Algorithmic Foundations of Differential Privacy. \textit{Foundations and Trends in Theoretical Computer Science}, 9(3-4), 211-407.

\item Ministry of Agriculture, Water Resources and Fisheries, Tunisia. (2020). \textit{Agricultural Statistics Yearbook}. Tunis: Republic of Tunisia.

\item IPCC. (2021). \textit{Climate Change 2021: The Physical Science Basis}. Contribution of Working Group I to the Sixth Assessment Report of the Intergovernmental Panel on Climate Change. Cambridge University Press.

\item Lobell, D. B., \& Field, C. B. (2007). Global scale climate–crop yield relationships and the impacts of recent warming. \textit{Environmental Research Letters}, 2(1), 014002.

\item Fielding, R. T. (2000). \textit{Architectural Styles and the Design of Network-based Software Architectures} (Doctoral dissertation). University of California, Irvine.

\item Fowler, M. (2002). \textit{Patterns of Enterprise Application Architecture}. Addison-Wesley Professional.

\item Newman, S. (2015). \textit{Building Microservices: Designing Fine-Grained Systems}. O'Reilly Media.

\item Kleppmann, M. (2017). \textit{Designing Data-Intensive Applications: The Big Ideas Behind Reliable, Scalable, and Maintainable Systems}. O'Reilly Media.

\item Gamma, E., Helm, R., Johnson, R., \& Vlissides, J. (1994). \textit{Design Patterns: Elements of Reusable Object-Oriented Software}. Addison-Wesley Professional.

\item Osmani, A. (2017). \textit{Learning JavaScript Design Patterns} (2nd ed.). O'Reilly Media.

\item OWASP Foundation. (2021). \textit{OWASP Top Ten Web Application Security Risks}. Available at: \url{https://owasp.org/www-project-top-ten/}

\item W3C. (2018). \textit{Web Content Accessibility Guidelines (WCAG) 2.1}. Available at: \url{https://www.w3.org/TR/WCAG21/}

\item European Commission. (2016). \textit{General Data Protection Regulation (GDPR)}. Official Journal of the European Union.

\end{itemize}

\vspace{2cm}

\addcontentsline{toc}{chapter}{References}
