\section*{\centering \Huge \textbf{ACKNOWLEDGMENTS}} 

\vspace{2cm}

With profound gratitude, I wish to acknowledge the unwavering support and inspiration that have illuminated my path throughout this transformative project.

First and foremost, I extend my deepest appreciation to my family. Your constant encouragement, understanding, and sacrifices have been the bedrock of my endeavors. Thank you for believing in me, even when challenges seemed insurmountable, and for providing a nurturing environment where I could thrive. Your love has been my guiding star, and I am eternally grateful.

To my esteemed academic supervisor, \textbf{Prof. Montassar Ben Messaoud, Ph.D.}, I offer my sincerest thanks. Your exceptional guidance, insightful feedback, and unwavering support were instrumental in shaping this project. You raised the bar for our learning journey, pushing us to explore the depths of Web Services with a rigor and passion that I have rarely encountered. The knowledge and skills I gained under your tutelage have been transformative, exceeding far beyond what I learned in any other course. Your emphasis on real-world applicability, technical excellence, and cultural preservation has profoundly influenced my approach to software engineering. Thank you for challenging us, inspiring us, and fostering a truly enriching learning experience. Your mentorship has been invaluable, and I am profoundly grateful for the opportunity to have learned from you.

I would also like to express my sincere gratitude to my friends and colleagues, who have been a constant source of motivation, laughter, and companionship throughout this journey. Thank you for your unwavering belief in me, for the countless hours of brainstorming sessions, debugging marathons, and for your willingness to lend an ear or offer a helping hand whenever needed. Special thanks to my classmates who provided valuable feedback during project presentations and helped refine my technical approach. Your presence has made this experience not only bearable but truly enjoyable.

I am deeply grateful to the Tunisian agricultural community, particularly the farmers, agronomists from INRAT, and conservatory experts who generously shared their knowledge of traditional agrarian calendars and provided invaluable domain expertise. Your insights into the challenges facing Tunisian agriculture and the cultural significance of traditional planting periods were instrumental in shaping this project's vision and ensuring its practical relevance.

Finally, I want to acknowledge my own perseverance and dedication. Completing this report has been a testament to my ability to overcome technical challenges, push beyond my perceived limits, and emerge stronger. From mastering Bayesian statistics to implementing differential privacy frameworks, from debugging complex API integrations to optimizing database queries, each obstacle has been a learning opportunity. I am proud of my commitment to this project and grateful for the growth it has fostered within me.

This report is not just the culmination of a project, but a reflection of the collective support, guidance, and inspiration I have received. I am deeply indebted to everyone who has contributed to this journey, and I hope this work serves as a fitting tribute to your unwavering belief in me and as a meaningful contribution to preserving Tunisia's agricultural heritage in the digital age.

\vspace{3cm}

\addcontentsline{toc}{chapter}{Acknowledgments}
